PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2023-04-27 main.tex
Fix broken references

\noindent \textbf{For bodies on circular, non-inclined orbits, $\tilde{b} = 2 \sqrt{3}$ is the smallest orbital separation that produces a non-negative
Jacobi energy and permits a close encounter \citep{nakazawa88}. This value of $\tilde{b}$ is typically used to calculate the final isolation mass of a protoplanet, as oligarchic growth tends to ensure that embryos stay on near-circular orbits as they grow.}

@@

In figure \ref{fig:timescales}, we show the ratio between the relaxation
and collision timescale for a population of equal-mass planetesimals
as a function of orbital period. Here, the encounter velocity is
described by equation \ref{eq:ecc_vel}. For
simplicity, we assume that $\left< e^2 \right>^{1/2} = 2\left< i^2
\right>^{1/2}$ \citep{ida93a} and that the eccentricity dispersion is
constant with orbital period. \textbf{The coloring indicates the ratio between
$t_{relax}$ and $t_{coll}$. The dashed lines denote the eccentricity at which the
random encounter velocity (calculated according to equation \ref{eq:ecc_vel}) is
equal to the mutual escape velocity of the bodies. This is shown for planetesimals
with an internal density of $3 g cm^{-3}$ ranging from 10 to 200km in size.}

@@

The timescales for embryo formation depend on
the chosen surface density profile, along with the local orbital
timescale. Protoplanets form first at the inner edge of the disk,
where the dynamical timescales are short. Growth proceeds in an
inside-out fashion, with the outermost regions of the disk completing
the protoplanet assembly phase last \textbf{(as an example, see figure 1 of \citet{kokubo02)}}. This radial timescale dependence is not typically
accounted for in planet formation simulations \textbf{(a notable exception being \citet{emsenhuber21a, emsenhuber21b})}, and appears to be an
important component to forming realistic solar system analogs
\citep{clement20}. As with the narrow annulus simulations, we stop the
integration once the masses of protoplanets in the outermost region of
the disk reach a steady value. In table \ref{tab:sim_properties}, we
summarize the outcomes of the four ``full disk'' cases.

We show the final state of the ``fdHi'' simulation in figure \ref{fig:fulldisk_e_m}. In the top panel,
the initial (contours) and final (points) state of the simulation is
shown in the orbital period-eccentricity plane. The size of the points
indicates the relative mass of the bodies. In the bottom panel, the
final masses of the bodies (in units of feeding zone size) are shown
as a function of orbital period. \textbf{The y-values in the bottom panel of figure \ref{fig:fulldisk_e_m} are calculated by solving equation \ref{eq:iso2} for $\tilde{b}$, and inputting the initial surface density and final particle mass into the expression.} Here, we assume that each embryo has reached its isolation mass, and 
that differences in mass are driven by differences in the initial surface density at the embryo's current location, along with the 
size of its feeding zone, which is set by the dynamics relevant at that location in the disk. By plotting the derived value of $
\tilde{b}$ as a function of orbital period, differences in the dynamical interactions at different locations of the disk are made more 
clearly visible. \textbf{The feeding zone size $\tilde{b} = 2 \sqrt{3}$ permitted by bodies on circular, non-inclined orbits \citep{nazakawa88} is shown by the
horizontal dashed line.} In typical oligarchic growth simulations \citep{kokubo98}, protoplanets tend 
to space themselves apart by $\tilde{b} = 10$, although it should be noted that they do not consume all of the planetesimals 
within this distance.

>>>>

\noindent \textbf{For bodies on circular, non-inclined orbits, $\tilde{b} = 2 \sqrt{3}$ is the smallest orbital separation that produces a non-negative
Jacobi energy and permits a close encounter \citep{naka88}. This value of $\tilde{b}$ is typically used to calculate the final isolation mass of a protoplanet, as oligarchic growth tends to ensure that embryos stay on near-circular orbits as they grow.}

@@

In figure \ref{fig:timescales}, we show the ratio between the relaxation
and collision timescale for a population of equal-mass planetesimals
as a function of orbital period. Here, the encounter velocity is
described by equation \ref{eq:ecc_vel}. For
simplicity, we assume that $\left< e^2 \right>^{1/2} = 2\left< i^2
\right>^{1/2}$ \citep{ida93a} and that the eccentricity dispersion is
constant with orbital period. \textbf{The coloring indicates the ratio between
$t_{relax}$ and $t_{coll}$. The dashed lines denote the eccentricity at which the
random encounter velocity (calculated according to equation \ref{eq:ecc_vel}) is
equal to the mutual escape velocity of the bodies. This is shown for planetesimals
with an internal density of 3 g $cm^{-3}$ ranging from 10 to 200 km in size.}

@@

The timescales for embryo formation depend on
the chosen surface density profile, along with the local orbital
timescale. Protoplanets form first at the inner edge of the disk,
where the dynamical timescales are short. Growth proceeds in an
inside-out fashion, with the outermost regions of the disk completing
the protoplanet assembly phase last \textbf{(as an example, see figure 1 of \citet{kokubo02}}. This radial timescale dependence is not typically
accounted for in planet formation simulations \textbf{(a notable exception being \citet{emsenhuber21a, emsenhuber21b})}, and appears to be an
important component to forming realistic solar system analogs
\citep{clement20}. As with the narrow annulus simulations, we stop the
integration once the masses of protoplanets in the outermost region of
the disk reach a steady value. In table \ref{tab:sim_properties}, we
summarize the outcomes of the four ``full disk'' cases.

We show the final state of the ``fdHi'' simulation in figure \ref{fig:fulldisk_e_m}. In the top panel,
the initial (contours) and final (points) state of the simulation is
shown in the orbital period-eccentricity plane. The size of the points
indicates the relative mass of the bodies. In the bottom panel, the
final masses of the bodies (in units of feeding zone size) are shown
as a function of orbital period. \textbf{The y-values in the bottom panel of figure \ref{fig:fulldisk_e_m} are calculated by solving equation \ref{eq:iso2} for $\tilde{b}$, and inputting the initial surface density and final particle mass into the expression.} Here, we assume that each embryo has reached its isolation mass, and 
that differences in mass are driven by differences in the initial surface density at the embryo's current location, along with the 
size of its feeding zone, which is set by the dynamics relevant at that location in the disk. By plotting the derived value of $
\tilde{b}$ as a function of orbital period, differences in the dynamical interactions at different locations of the disk are made more 
clearly visible. \textbf{The feeding zone size $\tilde{b} = 2 \sqrt{3}$ permitted by bodies on circular, non-inclined orbits \citep{naka88} is shown by the
horizontal dashed line.} In typical oligarchic growth simulations \citep{kokubo98}, protoplanets tend 
to space themselves apart by $\tilde{b} = 10$, although it should be noted that they do not consume all of the planetesimals 
within this distance.
